\documentclass[10 pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{multicol}
\usepackage{xcolor}

\usepackage{graphicx}
\usepackage{amsmath,amssymb}
\usepackage{subfig}
\usepackage{float}
\usepackage{enumitem}

\newcommand{\mypartitle}[2][2.]{\vspace*{-#1 ex}~\\{\noindent {\bf #2}}}

% Change font to sans serif
\renewcommand{\familydefault}{\sfdefault}

\title{\textbf{Angel Noé Martínez-González}}
%\author{Angel Martinez-Gonzalez}
\date{}

\usepackage[width=170mm,left=20mm,paperwidth=210mm,height=267mm,top=15mm,paperheight=297mm]{geometry}

\begin{document}
\maketitle
\vspace{-1.5cm}

\begin{minipage}[t]{0.4\linewidth}

\hspace{-0.5cm}\textbf{Contact}

\begin{itemize}[noitemsep]

\item[Mobile:] +41 76 823 3671
\item[E-mail:] angelmtzg.09@gmail.com

\end{itemize}

\end{minipage}

\bigskip

\mypartitle{Current position}\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}{.1\textwidth}

\vspace{-1cm}
\hspace{-.5cm}\textbf{11.16-}

\end{minipage}\begin{minipage}{0.87\textwidth}

PhD student in the Doctoral School of Electrical Engineering at Ecole Polytechnique
Federal de Lausanne (EPFL), Switzerland and research assistant in the Perception Group
at Idiap Research Institute, Switzerland under the supervision of Dr. Jean-Marc Odobez.

\end{minipage}\\

\medskip
\medskip

\mypartitle{Education}
\medskip
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\hrule
\medskip

\begin{minipage}[t]{.1\textwidth}

\vspace{-.5cm}
\hspace{-.5cm}\textbf{2012-14}

\end{minipage}\begin{minipage}{0.87\textwidth}

\textbf{Master in Computer Science}. Center for Research in Mathematics (CIMAT), México. 
Cumulative Grade Point Average: 92/100.

\end{minipage}\\

\begin{minipage}{.1\textwidth}

\vspace{-.5cm}
\hspace{-.5cm}\textbf{2007-12}

\end{minipage}\begin{minipage}{0.87\textwidth}

\textbf{Computer Systems Engineering}. Engineering Division, University of Guanajuato, 
Mexico. Cumulative Grade Point Average: 89/100. Specialization: Artificial Intelligence 
and Industrial Informatics. 

\end{minipage}\\

\medskip
\medskip

\mypartitle{Work Experience}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\medskip
\hrule
\medskip
\begin{minipage}[t][2cm]{0.1\textwidth}

\hspace{-.5cm}\textbf{2012, 2016}

\end{minipage}\begin{minipage}[t][2cm]{0.87\textwidth}

\textbf{Research and Development Engineer}. Center for Research in Mathematics (CIMAT), México. 
Machine learning and computer vision techniques (C/C++, python). 
Design, planning, development and deployment of:
1) computer graphics algorithms for gaming with virtual reality, collaboration with GameCoder Studios, Mexico,
2) automatic image recognition system for mobile devices,
3) object tracking system for the NAO robotic platform for the Robocup 2012.


\end{minipage}
\medskip

\begin{minipage}[t][1.1cm]{0.1\textwidth}

\hspace{-.5cm}\textbf{2015}

\end{minipage}\begin{minipage}[t][1.1cm]{0.87\textwidth}

\textbf{Software Engineer}. Intel Corporation (Intel-GDC), México. Development, maintaining,
troubleshooting and automation of the Android camera stack for Intel mobile products (C/C++/python/bash).

\end{minipage}
\medskip

\begin{minipage}[t][1.1cm]{0.1\textwidth}

\hspace{-.5cm}\textbf{2014}

\end{minipage}\begin{minipage}[t][1.4cm]{0.87\textwidth}

\textbf{Research internship}. Laboratory for Analysis of Architectures and Systems (LAAS-CNRS), France. 
Modeling and development of an automatic system for video surveillance using machine learning. 
Working with a physical surveillance camera network to acquire information of daily activities 
(C/C++/python).

\end{minipage}
\medskip

\begin{minipage}[t][.7cm]{0.1\textwidth}

\hspace{-.5cm}\textbf{2013-14}

\end{minipage}\begin{minipage}[t][.7cm]{0.87\textwidth}

\textbf{Teaching Assistant}. Center for Research in Mathematics (CIMAT), México.
Applied Probability and Statistic MSc course.
Instructional responsibilities, grading and recording scores, teaching R.

\end{minipage}
\medskip

%\begin{minipage}{0.1\textwidth}
%
%\vspace{-1cm}
%\hspace{-.5cm}\textbf{2011-12}
%
%\end{minipage}\begin{minipage}{0.9\textwidth}
%
%Research in human activity recognition, Laboratory for Vision, Robotics and Artificial
%Intelligence (LaViRIA), University of Guanajuato, México. Reviewing the state of the art and
%techniques in the subject. Implementing modules in C/C++ for testing new research theories.
%
%\end{minipage}

\begin{minipage}[t][.7cm]{0.1\textwidth}

\hspace{-.5cm}\textbf{2012-13}

\end{minipage}\begin{minipage}[t][.7cm]{0.87\textwidth}

\textbf{Science diffusion}. Center for Research in Mathematics (CIMAT), México.
Programming sessions of SCRATCH for children at secondary school level.

\end{minipage}
\medskip

\begin{minipage}[t][.7cm]{0.1\textwidth}

\hspace{-.5cm}\textbf{2003-08}

\end{minipage}\begin{minipage}[t][.7cm]{0.87\textwidth}

\textbf{Adult Education}. National Institute for Adult Education (INEA), México.
Tutoring sessions and direction of exams for adult certification of basic education.

\end{minipage}\\

\medskip
\medskip

\mypartitle{Research}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\medskip
\hrule
\medskip

\begin{minipage}{0.1\textwidth}

\textbf{Interests}

\end{minipage}\begin{minipage}{0.9\textwidth}

Human-computer interaction, video analysis, machine learning.

\end{minipage}

\begin{itemize}[noitemsep]


\item Michael Villamizar, Angel Martinez-Gonzalez, Olivier Canevet and Jean-Marc Odobez.
WatchNet: Efficient and Depth-based Network for People Detection inVideo Surveillance Systems
IEEE Int. Conf. on Advanced Video and Signal-Based Processing (AVSS), 2018
\vspace{.05cm}
%
%Angel Martinez-Gonzalez, Michael Villamizar, Olivier Canevet and Jean-Marc Odobez.
%Efficient Convolutional Neural Networks for Human Pose Estimation.
%IEEE Transactions on Systems and Circuits for Video Technology (submitted for revision), 2019.

\item  Angel Martinez-Gonzalez, Michael Villamizar, Olivier Canevet and Jean-Marc Odobez.
Investigating Domain Adaptation for Efficient Human Pose Estimation.
European Conference on Computer Vision - Workshops, (ECCV) 2018.
\vspace{.05cm}

\item Angel Martinez-Gonzalez, Michael Villamizar, Olivier Canevet and Jean-Marc Odobez.
Real-Time Convolutional Neural Networks for Depth-Based Human Pose Estimation.
IEEE/IRSJ Int. Conf. on Intelligent Robots and Systems (IROS), 2018.
\vspace{.05cm}

\item MSc. Thesis: “Motion-Based Camera-Network Topology Inference”, working with machine learning models and computer 
vision techniques in a visual surveillance framework. Thesis director: Dr. Jean-Bernard Hayet (CIMAT). 
Thesis co-director: Dr. Frédéric Lerasle (LAAS-CNRS).
\vspace{.05cm}

\item BSc. Thesis: “Human Activity Recognition using Soft Computing”, working with artificial neural networks, 
fuzzy systems and computer vision techniques. Thesis director: Dr. Victor Ayala Ramirez.
\vspace{.05cm}

\item Angel N. Martinez-Gonzalez and Victor Ayala-Ramirez. Real-time Face Detection Using Neural Networks. 
IEEE Mexican International Conference on Artificial Intelligence, (MICAI), 2011.
\vspace{.05cm}

\end{itemize}
%
%
%Poster, Image Processing Workshop, PI-14, CIMAT. Angel N. Martinez, Jean-Bernard Hayet
%and Frédéric Lease. Motion-Based Camera-Network Topology Inference.

\medskip
\medskip

\mypartitle{Skills}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\medskip
\hrule
\medskip

\begin{itemize}[noitemsep]
\item Development C/C++.
\item Scripting Python,  Matlab, R.
\item Operating systems: Windows (user), Linux (user).
\end{itemize}

\medskip
\medskip


\mypartitle{Projects}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\medskip
\hrule
\medskip

\begin{itemize}[noitemsep]

\item EU-H2020 MuMMER project.% Development of a system of automatic human pose estimation for social robotics.

\item ViZDoom with Reinforcement Learning. Solving navigation tasks in a 3d FPS game 
environment for autonomous agents with deep reinforcement learning methods.

\item 3d object culling methods for a virtual reality game: Sophie's guardian GameCoder Studios, Mexico.

\item Algorithms Analysis and Design Group. Intel Corporation, (Intel-GDC) Mexico. 
Informal speeches to cover some topics of algorithm design and analysis for the Intel community.

\item Human motion and gesture recognition for human-computer interaction in a augmented reality
system for product management.

\item Multi-person visual tracking. Center for Research in Mathematics (CIMAT), México. 
Development of a vision system able to track multiple people.

\item Ball tracking for the NAO robot for soccer playing in the Robocup soccer championship.

\item Real Time Face Detection. Development of a real time vision system able to detect human
faces in video.


\end{itemize}


\mypartitle{Awards and Grants}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\medskip
\hrule
\medskip

\begin{itemize}[noitemsep]

\item Scholarship for MSc and PhD studies, National Council for Science and Technology (CONACyT), México, 2012,2016.
\item 1st Place by Country University ranking, IEEExtreme programming competition, 2011.
\item Academic excellence for the best student of the generation, University of Guanajuato, 2011.
\item Outstanding performance student, Merit student award, University of Guanajuato, 2008, 2009, 2010.
\item Member of the student committee, Engineering Division, University of Guanajuato, 2009, 2010.

\end{itemize}



\mypartitle{Languages}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\medskip
\hrule
\medskip

Spanish: Mother tongue; English: Fluent; French: Intermediate; German: Basic.

\mypartitle{Referees}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\medskip
\hrule
\medskip

\begin{itemize}[noitemsep]

\item Dr. Jean-Marc Odobez, MER. EPFL, Switzerland: odobez@idiap.ch.
\item Dr. Frédéric Lerasle, Professor of the Paul Sabatier University and LAAS-CNRS: lerasle@laas.fr.
\item Dr. Jean-Bernard Hayet, Associate Researcher at CIMAT: jbhayet@cimat.mx.
\item Dr. Johan Van Horebeek, Associate Researcher at CIMAT: horebeek@cimat.mx.

\end{itemize}








\end{document}
